---
title: "Data Product Development - Final Presentation"
author: "Jinkwan Hong"
date: "2019/ 02/ 01"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(titanic)
library(datasets)
library(dplyr)
library(ggplot2)
train <- titanic_train
test <- titanic_test

## Preprocessing
### Factorizing
train$Pclass <- factor(train$Pclass)
train$Sex <- factor(train$Sex)
train$SibSp <- factor(train$SibSp)
train$Parch <- factor(train$Parch)
train$Embarked <- factor(train$Embarked)
train$Survived <- factor(train$Survived)
test$Pclass <- factor(test$Pclass)
test$Sex <- factor(test$Sex)
test$SibSp <- factor(test$SibSp)
test$Parch <- factor(test$Parch)
test$Embarked <- factor(test$Embarked)

classChoices <- c(unique(levels(train$Pclass)))
sexChoices <- c(unique(levels(train$Sex)))
sibspChoices <- c(unique(levels(train$SibSp)))
parchChoices <- c(unique(levels(train$Parch)))
embarkedChoices <- c(unique(levels(train$Embarked)))
variableChoices <- c("Pclass","Sex","Embarked")
```

## Overview

### Intoduction

- Explore titanic incident data with many variables
- Allow users to explore data and do basic EDA easily
- Explain how to use the application

Application URL: https://jinkwanh.shinyapps.io/titanic/
Presentation URL: https://jiinkwan.github.io/week2/titanic/Titanic_Presentation.htm
Source Code URL: https://github.com/jiinkwan/week2/blob/gh-pages/titanic/

## Main Panel

- Survival rates summary within the specific group
- Interactive bar plot to summarize how many people survived or perished
- Table data to see the detail of the people

## Plot

```{r echo = FALSE}
    g <- ggplot(train, aes_string(train$Pclass))                    
    g <- g + geom_bar(aes(fill=train$Survived), width = 0.5) + theme(axis.text.x = element_text(angle=65, vjust=0.6)) + labs(title="Survivors")
    g
```

## Side Panel

- Select variable to control the plot
- Filter out the information to display
- Class: which class of cabin the pessenger had
- Sex: male or female
- SibSp: Number of siblings and spouses within the cruize
- Parch: Number of parents and children within the cruize
- Embarked: Where the pessengers got on the cruize(C = Cherbourg, Q = Queenstown, S = Southampton)
